Results visualization across sites

### 2021-12-02 metanalysis_visualization/visualization.Rmd
visualization code updated: new plot for apendix for the psychiatric ICD codes dictionary QC

### Summary of the codes used per site 
```{r}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) )

@@

### UpSet R for each disorder group
```{r}
disorders <- unique( mental_codes_qc_output_all$disorder_group)
for( i in 1:length(disorders) ){
  print( disorders[i] )
  upsetForDisorderGroup( df = mental_codes_qc_output_all, disorderGroup = disorders[i])
}
```

>>>>

### Summary of the codes used per site 
```{r}
mental_codes_qc_output_all <- mental_codes_qc_output_all %>%
    mutate( concept_code = gsub("[.]", "", concept_code ) ) %>%
  unique()

@@

### Estimate number of ICD codes per site and disorder group
Represent this in 16 pannels, if we put all together, due to the different scales we will not be able to really see the differences between results. 
```{r}
numberOfCodesPerDisorderGroup <- mental_codes_qc_output_all %>%
  group_by( disorder_group, siteid ) %>%
  mutate( icd_codes_count = n( )) %>%
  select( disorder_group, siteid, icd_codes_count ) %>%
  unique()

swr = function(string, nwrap=30) {
  paste(strwrap(string, width=nwrap), collapse="\n")
}
swr = Vectorize(swr)

numberOfCodesPerDisorderGroup %>%
  mutate( disorder_group = swr( disorder_group ) ) %>%
  ggplot( aes( x= reorder( siteid, icd_codes_count), y = icd_codes_count)) +
  geom_bar( stat = "identity") +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  labs(x ="site identifier", y = "ICD dictionary (number of ICD codes)") +
  theme(axis.text.x=element_text(angle=45,hjust=1, size = 6), 
        strip.text = element_text(size = 7), 
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
```
